### 2020-04-28 templates/Materials_and_methods__Data_visualization.Rmd
Fix typo

#<EN>
cap <- "Correlations at each age"
f_lvl <- c("3 days", "7 days", "14 days","28 days", "56 days", "100 days")
name <- "Correlation"
colnames_dat <- c("Cement", "B.F.S.", "Fly ash", "Water",
                "Superplast.", "Coarse agg.", "Fine agg.", "3", "7",
                "14", "28", "56", "100",
                "W./C.", "F.A./C.", 
                "C.A./C.", "F.A./C.A.",
                "W./C.A.", "W./F.A.")
#</EN>
#<PT>
cap <- "Correlações em cada idade"
f_lvl <- c("3 dias", "7 dias", "14 dias","28 dias", "56 dias", "100 dias")
name <- "Correlação"
colnames_dat <- c("Cimento", "E.G.A.F.", "C.Volante", "Água",
                  "Superp.", "A.Graúdo", "A.Miúdo",
                  "3","7","14","28","56","100",
                  "class","mix_app" ,"Ág./Ci.",
                  "A.M./Ci.", "A.G./Ci.", "A.M./A.G.",
                  "Ág./A.G.", "Ág./A.M.")
#</PT>

>>>>

#<EN>
cap <- "Correlations at each age"
f_lvl <- c("3 days", "7 days", "14 days","28 days", "56 days", "100 days")
name <- "Correlation"
colnames_dat <- c("Cement", "B.F.S.", "Fly ash", "Water",
                "Superplast.", "Coarse agg.", "Fine agg.",
                "3", "7", "14", "28", "56", "100",
                "class", "mix_app", "W./C.", "F.A./C.", 
                "C.A./C.", "F.A./C.A.",
                "W./C.A.", "W./F.A.")
#</EN>
#<PT>
cap <- "Correlações em cada idade"
f_lvl <- c("3 dias", "7 dias", "14 dias","28 dias", "56 dias", "100 dias")
name <- "Correlação"
colnames_dat <- c("Cimento", "E.G.A.F.", "C.Volante", "Água",
                  "Superp.", "A.Graúdo", "A.Miúdo",
                  "3","7","14","28","56","100",
                  "class","mix_app" ,"Ág./Ci.",
                  "A.M./Ci.", "A.G./Ci.", "A.M./A.G.",
                  "Ág./A.G.", "Ág./A.M.")
#</PT>
